Belowground sink limitation alters growth and carbon balance of *Eucalyptus* seedlings

### 2016-01-15 manuscript/manuscript_pve.Rmd
updates cites, sent this manuscript version to BM

---
title: Belowground sink limitation alters growth and carbon balance of *Eucalyptus* seedlings
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle_thesis.docx
  pdf_document: default
  html_document:
    number_sections: yes

csl: tree-physiology.csl
bibliography: references.bib
---

>>>>

---
title: Belowground sink limitation alters growth and carbon balance of *Eucalyptus* seedlings
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle.docx
  pdf_document: default
  html_document:
    number_sections: yes

csl: tree-physiology.csl
bibliography: references2.bib
---
